---
title: "National Acceptance of LGBT Identities & Voting Likelihood"
author: "Lulu August (she/her)"
description: "Gov50 Final Project, December 2022"
output:
  distill::distill_article:
    self_contained: false
---

# Introduction



# Data Description

##### Data Wrangling

```{r loading packages}
library(foreign)
library(tidyverse)
library(broom)
```

```{r, echo=FALSE}
lgbt <- read.spss("pew2013lgbtpublicdatarelease.sav", to.data.frame=TRUE)
```


```{r data wrangling}
lgbt_data <- lgbt |>
  select(OFTVOTE, Q53, SEX, Q71, PPEDUCAT) |>
  rename(oft_vote = OFTVOTE,
         nat_acceptance = Q53,
         sex = SEX,
         loc_acceptance = Q71,
         ed = PPEDUCAT) |>
  mutate(nat_acceptance_mod = case_when(
    nat_acceptance == "None at all" ~ 0,
    nat_acceptance == "Only a little" ~ 1,
    nat_acceptance == "Some" ~ 2,
    nat_acceptance == "A lot" ~ 3
  )) |>
  mutate(oft_vote_mod = case_when(
    oft_vote == "Seldom" ~ 0,
    oft_vote == "Part of the time" ~ 1,
    oft_vote == "Nearly always" ~ 2,
    oft_vote == "Always" ~ 3
  )) |>
  mutate(sex_mod = if_else(sex == "Female", 1, 0)
  ) |>
  mutate(ed_mod = if_else(ed == "Bachelor's degree or higher", 1, 0)
    ) |>
  mutate(loc_acceptance_mod = case_when(
    loc_acceptance == "None at all" ~ 0,
    loc_acceptance == "Only a little" ~ 1,
    loc_acceptance == "Some" ~ 2,
    loc_acceptance == "A lot" ~ 3
  )) |>
  select(nat_acceptance_mod, oft_vote_mod, sex_mod, ed_mod, loc_acceptance_mod) |>
  drop_na()
head(lgbt_data)
```


##### Barplot of Dependent Variable
```{r barplot of dependent variable}
ggplot(data = lgbt_data, mapping = aes(x = factor(oft_vote_mod))) +
  geom_bar() +
  labs (x = "Number of People in Different Voting Likelihoods",
        y = "Number of People",
        title = "Voting Likelihood")
```
```{r}
n_zero_vote <- lgbt_data |>
  filter(oft_vote_mod == 0)
print(nrow(n_zero_vote))

n_one_vote <- lgbt_data |>
  filter(oft_vote_mod == 1)
print(nrow(n_one_vote))

n_two_vote <- lgbt_data |>
  filter(oft_vote_mod == 2)
print(nrow(n_two_vote))

n_three_vote <- lgbt_data |>
  filter(oft_vote_mod == 3)
print(nrow(n_three_vote))
```

# Results

##### Boxplot of Main Relationship of Interest
```{r boxplot of independent and dependent variable}
ggplot(data = lgbt_data, mapping = aes(x = factor(nat_acceptance_mod),
                                       y = oft_vote_mod)) +
  geom_boxplot() +
  labs(
    x = "Feelings of National Acceptance of LGBT Identity")
```

##### One Variable Linear Regression
```{r}
regression <- lm(oft_vote_mod ~ nat_acceptance_mod, data = lgbt_data)

modelsummary::modelsummary(regression,
                           statistic = c("s.e. = {std.error}",
                                         "p = {p.value}"),
                           gof_map = c("nobs", "r.squared", "adj.r.squared"))
```

##### Multiple Variable Regression
```{r}
multi_regression <- lm(oft_vote_mod ~ nat_acceptance_mod + sex_mod + ed_mod + loc_acceptance_mod, data = lgbt_data)

modelsummary::modelsummary(multi_regression,
                           statistic = c("s.e. = {std.error}",
                                         "p = {p.value}"),
                           gof_map = c("nobs", "r.squared", "adj.r.squared"))
```


# Conclusion

# Bibliography
"About Pew Research Center." Pew Research Center, www.pewresearch.org/about/.

Cherry, Kendra. "How Do Cross-Sectional Studies Work?" Very Well Mind, www.verywellmind.com/what-is-a-cross-sectional-study-2794978.

George, Tegan. "What Is an Observational Study? | Guide & Examples." Scribbr, 31 Mar. 2022, www.scribbr.com/methodology/observational-study/.

Suh, Michael. 2013 Survey of LGBT Adults. 18 Sept. 2014. Pew Research Center, www.pewresearch.org/social-trends/2014/09/18/2013-survey-of-lgbt-adults/.

"Voter Turnout." FairVote, fairvote.org/resources/voter-turnout/#what-affects-voter-turnout.
